FDT\thanks{Supported by organization x.}

### 2018-11-18 IPCO format/FDT.tex
shorter version

A analogous result to Proposition \ref{cara} is the following theorem due to Carr and Vempala \cite{CV}.

@@

\begin{question}\label{question2}
	Assume reasonable complexity assumptions, a specific problem $\mathcal{I}$ with  $1<g_{\mathcal{I}}<\infty$, and $(x,y)\in P(I)$ for some $I\in \mathcal{I}$, can we find $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $(\tilde{x}^i,\tilde{y}^i)\in S(I)$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq g_{\mathcal{I}}x$ in polynomial time?
\end{question}
Although Question \ref{question2} is wide open, for some problems $\mathcal{I}$ there are polynomial time algorithms. For example, for generalized Steiner forest problem \cite{jain} gave an LP-based 2-approximation algorithm. The gap for this problem is also lower bounded by 2. Same holds for the set covering problem \cite{randomizedrounding}. In fact, for set cover the approximation algorithm achieving the same factor as the integrality gap lower bound, is a \textit{randomized rounding} algorithm. Rhagavan and Thompson \cite{randomizedrounding} showed that this technique acheives provably good approximation for many combinatorial optimization problems.

One key step, in answering Question \ref{question1} and \ref{question2} is being able to find a solution in $S(I)$. In fact, for general $I$ it is NP-hard to even decide if $S(I)$ is empty or not. There are a number of heuristics for this purpose, such as the feasibility pump heuristic \cite{fp1,fp2}. These heuristics are often very effective and fast in practice, however, they can sometimes fail in finding a feasible solution. In addition these algorithms do not provide any bounds on the quality of the solution they find.

\subsection{Our results}

In this paper we study Theorem \ref{CV} and the natural questions that follow from it (Questions \ref{question1} and \ref{question2}).

We give a general approximation framework for solving $\{0,1\}$-MILPs.  Consider the set of point described by a set 
\begin{equation}
S(I)= \{(x,y)\in \bbbr^{n\times p}\;:\; Ax+Gy\geq b,\; x\in \{0,1\}\},  \label{S'}
\end{equation}
and a linear relaxation of set $S$
\begin{equation}
P(I) = \{(x,y)\in \bbbr^{n\times p}\;:\; Ax+Gy\geq b,\; 0 \leq x\leq 1\}. \label{P'}
\end{equation}
For a point $(x,y)\in P(I)$, let $\sup(x,y)= \{i \in \{1,\ldots,n\}: x_i \neq 0\}$.  We prove the following algorithm.

\begin{restatable}{theorem}{binaryFDT}
	\label{binaryFDT}
	Assume $1\leq g_I<\infty$. 	
	The FDT algorithm (Algorithm \ref{FDTFull}), given $(x^*,y^*)\in P(I)$, produces in polynomial time $\lambda\in [0,1]^k$ and $(z^1,w^1),\ldots,(z^k,w^k) \in S(I)$ such that $k\leq |\sup(x^*,y^*)|$, $\sum_{i=1}^{k}\lambda_i z^i\leq Cx^*$, and $\sum_{i=1}^{k}\lambda_i = 1$. Moreover, $C\leq g_I^{|\sup(x^*,y^*)|}$.
\end{restatable}

Notice, that the FDT algorithm needs to find feasible solutions to any MILP with finite gap. This can be of independent interest.
\begin{restatable}{theorem}{DomToIP}
	\label{DomToIP}
	Assume $1\leq g_I \leq \infty$. The DomToIP algorithm (Algorithm \ref{domtoIP}) finds $(\hat{x},\hat{y})\in S(I)$ in polynomial time.
\end{restatable}

In attempt to extend our results into $\{0,1,2\}$-MILPs we give an FDT algorithm for the 2-edge-connected multigraph problem. In this problem we want to find the minimum weight 2-edge-connected multigraph in a graph $G=(V,E)$ with respect to weights $c\in \bbbr^E_{\geq 0}$. For this problem the natural linear programming relaxation is
\begin{equation}\label{2ECpol}
\EC(G)= \{x\in \bbbr_{\geq 0}^{E}\;:\; x(\delta(S))\geq 2 \text{ for $\emptyset \subset S\subset V$})\}.\end{equation}
We prove the following theorem.

@@

\subsection{Notation}
For vectors $x,y\in \bbbr_{n}$ we say $x$ dominates $y$ if $x_i\geq y_i$ for $i= 1,\ldots,n$. For $m\times n$ matrix $A$, let $A_j$ be the $j$-th row of $A$ and $A^j$ be the $j$-th column of $A$. Let $\textbf{1}$ be the vector of all ones of a suitable dimension. For a set $S$ of vectors in $\bbbr_{n}$, $\conv(S)$ is the convex hull of all the points in $S$.

@@

Consider a formulation instance $I=(A,G,b)$, set 
\begin{equation}
S(I)= \{(x,y)\in \bbbr^{n\times p}\;:\; Ax+Gy\geq b,\; x\in \{0,1\}\},  \label{S'}
\end{equation}
and its linear relaxation
\begin{equation}
P(I) = \{(x,y)\in \bbbr^{n\times p}\;:\; Ax+Gy\geq b,\; 0 \leq x\leq 1\}. \label{P'}
\end{equation}
Also assume we are given a point $(x^*,y^*)\in P(I)$. For instance, $(x^*,y^*)$ can be the optimal solution of minimizing a cost function $cx$ over set $P$, which provides a lower bound on $\min_{(x,y)\in S(I)} cx$. In this section, we prove the following theorem.

\binaryFDT*

One key ingredient in proving Theorem \ref{binaryFDT} is Theorem \ref{DomToIP} that we will also prove in this section.

Although the theoretical worst-case upper bound on $C$ in the statement of Theorem \ref{binaryFDT} can be very large, we will show that in practice $C$ can be really small and hence FDT can provide good LP-based approximation algorithms in many cases. We also remark that if $g_I=1$, then the algorithm will give an exact decomposition of any feasible solution.  In the remainder of this section we explain the FDT algorithm and prove Theorem \ref{binaryFDT}. For simplicity in the notations we denote $P(I),S(I),$ and $g_I$ with $P,S,$ and $g$, respectively. Let $t=|\sup(x^*,y^*)|$. We assume without loss of generality that $\sup(x^*,y^*)= \{1,\ldots,t\}$.

We begin with the following lemmas that show how the FDT algorithm branches on a variable.
\begin{lemma}\label{LPClemma}
	Given $(x',y')\in \dom(P)$ and $\ell\in \{1,\ldots,n\}$, we can find in polynomial time vector $(\hat{x}^0,\hat{y}^0),(\hat{x}^1,\hat{y}^1)$ and scalars $\gamma_0,\gamma_1 \in [0,1]$ such that
	\begin{itemize}
		\item[(i)] $\gamma_0 + \gamma_1  \geq \frac{ 1}{g}$,
		\item[(ii)] $(\hat{x}^0,\hat{y}^0)$ and $(\hat{x}^1,\hat{y}^1)$ are in  $ P$, 
		\item[(iii)] $\hat{x}^0_\ell=0$ and $\hat{x}^1_\ell=1$,
		\item[(iv)] $\gamma_0 \hat{x}^0 + \gamma_1\hat{x}^1 \leq x'$.
	\end{itemize}
\end{lemma}

\begin{proof}[Proof of Lemma \ref{LPClemma}]

	Consider the following linear programing which we denote by $\LPC(\ell,x',y')$. The variables of $\LPC(\ell,x',y')$ are $\gamma_0,\gamma_1$ and $(x^0,y^0)$ and $(x^1,y^1)$. 
	\begin{align}
		\LPC(\ell,x',y')\quad\quad& \max\quad \;\lambda_0+\lambda_1\\
		&\;\text{s.t.} \quad Ax^j + Gy^j\geq b\lambda_j & \mbox{ for $j=0,1$} \label{feasibility}\\
		&\;{\color{white}{\text{s.t.}} }\quad 0 \leq x^j \leq \lambda_j &\mbox{ for $j=0,1$}\label{bound}\\
		&\;{\color{white}{\text{s.t.}} }\quad x^0_\ell = 0,\; x^1_\ell =\lambda_1\label{branchcoordinate}\\
		&\;{\color{white}{\text{s.t.}} }\quad x^0 + x^1 \leq x'\label{packing}\\
		&\;{\color{white}{\text{s.t.}} }\quad \lambda_0,\lambda_1 \geq 0
	\end{align}

@@

		\begin{equation}\label{splitting}
		x'\geq \sum_{i=1}^{k}\frac{\theta_i}{g} \tilde{x}^i
		={\sum_{i\in [k]: \tilde{x}^i_\ell =0}\frac{\theta_i}{g} \tilde{x}^i}+{\sum_{i\in [k]: \tilde{x}^i_\ell =1}\frac{\theta_i}{g} \tilde{x}^i}
		\end{equation}
		For $j=0,1$, let $(x^j,y^j) = \sum_{i\in [k]:\tilde{x}^i_\ell=j} \frac{\theta_i}{g}(\tilde{x}^i,\tilde{y}^i)$. Also let $\lambda_0=\sum_{i\in [k]: \tilde{x}^i_\ell =0}\frac{\theta_i}{g}$ and $\lambda_1 = \sum_{i\in [k]: \tilde{x}^i_\ell =1}\frac{\theta_i}{g}$. Note that $\lambda_0+\lambda_1 = \frac{1}{g}$. Constraint \ref{packing} is satisfied by Inequality \ref{splitting}. Also, for $j=0,1$ we have
		\begin{equation}
		Ax^j+Gy^j = \sum_{i\in[k], \tilde{x}^i_\ell = j} \frac{\theta_i}{g} (A\tilde{x}^i + G\tilde{y}^i) \leq b \sum_{i\in[k], \tilde{x}^i_\ell = j} \frac{\theta_i}{g} = b\lambda_j.
		\end{equation}
		Hence, Constraints \ref{feasibility} holds. Constraint \ref{branchcoordinate} also holds since $x^0_\ell$ is obviously $0$ and $x^1_\ell= \sum_{i\in [k]: \tilde{x}^i_\ell = 1}\frac{\theta_i}{g}= \lambda_1$. The rest of the constraints trivially hold. 
	\end{proof}
	This concludes the proof.	
\end{proof}

We now show if $x'$ in the statement of of Lemma \ref{LPClemma} is partially integral, we can find solutions with more integral components.
\begin{lemma}\label{round-up}
	Given $(x',y')\in \dom(P)$, such that $x'_1,\ldots,x'_{\ell-1}\in \{0,1\}$ for some $\ell\geq 1$, we can find in polynomial time vector $(\hat{x}^0,\hat{y}^0),(\hat{x}^1,\hat{y}^1)$ and scalars $\gamma_0,\gamma_1 \in [0,1]$ such that
	\begin{itemize}
		\item[(i)] $\gamma_0 + \gamma_1  \geq\frac{ 1}{g}$,
		\item[(ii)] $(\hat{x}^0,\hat{y}^0)$ and $(\hat{x}^1,\hat{y}^1)$ are in  $\dom( P)$, 
		\item[(iii)] $\hat{x}^0_\ell=0$ and $\hat{x}^1_\ell=1$,
		\item[(iv)] $ \gamma_0\hat{x}^0 +\gamma_1 \hat{x}^1 \leq
		x'$,
		\item[(v)] $\hat{x}^i_j\in \{0,1\}$ for $i=0,1$ and $j=1,\ldots,\ell-1$.
	\end{itemize}
\end{lemma} 
\begin{proof}
	By Lemma \ref{LPClemma} we can find $(\bar{x}^0,\bar{y}^0)$, $(\bar{x}^1,\bar{y}^1)$, $\gamma_0$ and $\gamma_1$ that satisfy (i), (ii), (iii), and (iv). We define $\hat{x}^0$ and $\hat{x}^1$ as follows. For $i=0,1$, for $j=1,\ldots,\ell-1$, let $\hat{x}^i_j= \ceil{\bar{x}^i_j}$, for $j=\ell,\ldots,n$ let $\hat{x}^i_j = \bar{x}^i_j$. We now show that $(\hat{x}^0,\bar{y}^0)$, $(\hat{x}^1,\bar{y}^1)$, $\gamma_0$, and $\gamma_1$ satisfy all the conditions. Note that conditions (i), (ii), (iii), and (v) are trivially satisfied. Thus we only need to show (iv) holds. We need to show that $\gamma_0 \hat{x}^0_j+\gamma_1\hat{x}^1_j\leq gx'_j$. If $j=\ell,\ldots,n$, then this clearly holds. Hence, assume $j\leq \ell-1$. By the property of $x'$ we have $x'_j\in \{0,1\}$. If $x'_j= 0$, then by Constraint \ref{packing} we have $\bar{x}^0_j = \bar{x}^1_j=0$. Therefore, $\hat{x}^i_j=0$ for $i=0,1$, so (iv) holds. Otherwise if $x'_j = 1$, then we have
	\begin{equation*}\gamma_0\hat{x}^0_j+\gamma_1\hat{x}^1_j\leq \gamma_0+\gamma_1\leq 1\leq x'_j.\end{equation*}
	Therefore (v) holds.
\end{proof}
The FDT algorithm grows a tree similar to the classic branch-and-bound search tree for integer programs. Each node represents a partially integral vector $(\bar{x},\bar{y})$ in $\dom(P)$ together with a multiplier $\bar{\lambda}$. The solutions contained in the nodes of the tree become progressively more integral at each level. Leaves of the FDT tree contain solutions with integer values for all the $x$ variables that dominate a point in $P$. We will later see how we can turn these into points in $S$.

Let us define the FDT algorithm more formally. The algorithm maintains nodes $L_i$ in iteration $i$ of the algorithm. The nodes in $L_i$ correspond to the nodes in level $L_i$ of the FDT tree. The points in the leaves of the FDT tree, or $L_t$, are points in $\dom(P)$ and are integral for all integer variables.

\begin{lemma}\label{prune}
	There is a polynomial time algorithm that produces sets $L_0,\ldots,L_t$ of pairs of $(x,y)\in \dom(P)$ together with multipliers $\lambda$ with the following properties for $i=0,\ldots,t$. 
	\begin{itemize}
		\item[a.] If $(x,y)\in L_i$, then $x_j \in \{0,1\}$ for $j=1,\ldots,i$, i.e. the first $i$ coordinates of a solution in level $i$ are integral. 
		\item[b.] $\sum_{[(x,y),\lambda]\in L_i} \lambda\geq\frac{1}{g^i}$.
		\item[c.] $\sum_{[(x,y),\lambda]\in L_i}\lambda x \leq x^*$.
		\item[d.] $|L_i|\leq t$.
	\end{itemize}
\end{lemma}
\begin{proof}
	We prove this lemma using induction but one can clearly see how to turn this proof into a polynomial time algorithm. Let $L_0$ be the set that contains a single node (\textit{root of the FDT tree}) with $(x^*,y^*)$ and multiplier 1. It is easy to check all the requirements in the lemma are satisfied for this choice.

	Suppose by induction that we have constructed sets $L_0,\ldots,L_i$. Let the solutions in $L_i$ be $(x^j,y^j)$ for $j=1,\ldots,k$ and $\lambda_j$ be their multipliers, respectively. For each $j\in 1,\ldots,k$ by Lemma \ref{round-up} (setting $(x',y')= (x^j,y^j)$ and $\ell = i$) we can find $(x^{j0},y^{j0}), (x^{j1},y^{j1})$ and $\lambda^0_j$, $\lambda^1_j$ with the properties (i) to (v) in Lemma \ref{round-up}. Define $L'$ to be the set of node with solutions $(x^{j0},y^{j0}), (x^{j1},y^{j1})$ and multipliers  $\lambda_j\lambda^0_j$, $\lambda_j\lambda^1_j$, respectively, for $j=1,\ldots,k$.

	Notice that for each $j\in \{1,\ldots,k\}$ by property (v) in Lemma \ref{round-up} we have $x_\ell^{j0}, x_\ell^{j1}\in \{0,1\}$ for $\ell = 0,\ldots,i+1$. We also have
	\begin{align*}
		\sum_{[(x,y),\lambda]\in L'} \lambda & =  \sum_{j=1}^{k} \lambda_j\lambda^0_j+\lambda_j\lambda^1_j&\\
		& \geq \sum_{j=1}^{k} \frac{\lambda_j}{ g} & (\text{By property (i) in Lemma \ref{round-up}})\\
		& \geq \frac{1}{g} \sum_{[(x,y),\lambda]\in L_i}\lambda&\\
		& \geq \frac{1}{g^{i+1}}.&(\text{By induction hypothesis})	 
	\end{align*} 
	Also 
	\begin{align*}
		\sum_{[(x,y),\lambda]\in L'}\lambda x & =  \sum_{j=1}^{k} \lambda_j\big(\lambda^0_jx^{j0}+\lambda^1_jx^{j1}\big)&\\ 
		& \leq \sum_{j=1}^{k} \lambda_j x^j  & (\text{By property (iv) in Lemma \ref{round-up}})\\
		& \leq \sum_{[(x,y),\lambda]\in L_i}\lambda x&\\
		& \leq x^*.&(\text{By induction hypothesis})	 
	\end{align*} 
	Set $L'$ seems like a suitable candidate for $L_{i+1}$, however we can only ensure that $|L'|\leq 2k\leq 2t$, and might have $|L'|>t$. We call the following linear programming $\prun(L')$. Let $L' = \{[(x^1,y^1),\lambda_1],\ldots,[(x^k,y^k),\lambda_k]\}$. The variables of $\prun(L')$ is a scalar variable $\theta_j$ for each node $j$ in $L'$.

	\begin{align}
		\prun(L')\quad\quad& \max\quad \;\sum_{j=1}^{k} \theta_j\\
		&\;\text{s.t.} \quad \;\;\sum_{j=1}^{k} \theta_j x^j_i\leq x^*_i &\mbox{ for $i=1,\ldots,t$} \label{packs}\\
		&\;{\color{white}{\text{s.t.}} }\quad  \;\quad\quad\theta \geq 0\label{nonneg}
	\end{align}

>>>>

A analogous result to Proposition \ref{cara} is the following theorem due to Carr and Vempala \cite{CV}, which is a generalization of Goemans proof for blocking polyhedra \cite{goemans}.

@@

\begin{question}\label{question2}
	Assume reasonable complexity assumptions, a specific problem $\mathcal{I}$ with  $1<g_{\mathcal{I}}<\infty$, and $(x,y)\in P(I)$ for some $I\in \mathcal{I}$, can we find $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $(\tilde{x}^i,\tilde{y}^i)\in S(I)$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq g_{\mathcal{I}}x$ in polynomial time?
\end{question}
Although Question \ref{question2} is wide open, for some problems $\mathcal{I}$ there are polynomial time algorithms closing the gap. For example, for generalized Steiner forest problem \cite{jain} gave an LP-based 2-approximation algorithm. The gap for this problem is also lower bounded by 2. Same holds for the set covering problem \cite{randomizedrounding}. In fact, for set cover the approximation algorithm achieving the same factor as the integrality gap lower bound, is a \textit{randomized rounding} algorithm. Rhagavan and Thompson \cite{randomizedrounding} showed that this technique acheives provably good approximation for many combinatorial optimization problems.

One key step, in answering Question \ref{question1} and \ref{question2} is being able to find a solution in $S(I)$. In fact, for general $I$ it is NP-hard to even decide if $S(I)$ is empty or not. There are a number of heuristics for this purpose, such as the feasibility pump heuristic \cite{fp1,fp2}. These heuristics are often very effective and fast in practice, however, they can sometimes fail in finding a feasible solution. In addition these algorithms do not provide any bounds on the quality of the solution they find.
\subsection{Our results}
In this paper we study Theorem \ref{CV} and the natural questions that follow from it (Questions \ref{question1} and \ref{question2}).

We give a general approximation framework for solving $\{0,1\}$-MILPs.  Consider the set of point described by a set 
\begin{equation}
S(I)= \{(x,y)\in \bbbr^{n\times p}\;:\; Ax+Gy\geq b,\; x\in \{0,1\}\},  \label{S'}
\end{equation}
and a linear relaxation of set $S$
\begin{equation}
P(I) = \{(x,y)\in \bbbr^{n\times p}\;:\; Ax+Gy\geq b,\; 0 \leq x\leq 1\}. \label{P'}
\end{equation}
For a vector $x\in \bbbr^n$ such that $(x,y)\in P(I)$ for some $y\in \bbbr^p$, let $\spp(x)= \{i \in \{1,\ldots,n\}: x_i \neq 0\}$.  We prove the following algorithm.

\begin{restatable}{theorem}{binaryFDT}
	\label{binaryFDT}
	Assume $1\leq g_I 	<\infty$. 	
	The FDT algorithm, given $(x^*,y^*)\in P(I)$, produces in polynomial time $\lambda\in [0,1]^k$ and $(z^1,w^1),\ldots,(z^k,w^k) \in S(I)$ such that $k\leq |\spp(x^*)|$, $\sum_{i=1}^{k}\lambda_i z^i\leq Cx^*$, and $\sum_{i=1}^{k}\lambda_i = 1$. Moreover, $C\leq g_I^{|\spp(x^*)|}$.
\end{restatable}

Notice, that the FDT algorithm needs to find feasible solutions to any MILP with finite gap. This can be of independent interest.
\begin{restatable}{theorem}{DomToIP}
	\label{domtoIP}
	Assume $1\leq g_I < \infty$. The DomToIP algorithm finds $(\hat{x},\hat{y})\in S(I)$ in polynomial time.
\end{restatable}

In attempt to extend our results into $\{0,1,2\}$-MILPs we give an FDT algorithm for the 2-edge-connected multigraph problem. In this problem we want to find the minimum weight 2-edge-connected subgraph (which can multiple copies of each edge) in a graph $G=(V,E)$ with respect to weights $c\in \bbbr^E_{\geq 0}$. For this problem the natural linear programming relaxation is
\begin{equation}\label{2ECpol}
\EC(G)= \{x\in \bbbr_{\geq 0}^{E}\;:\; x(\delta(S))\geq 2 \text{ for $\emptyset \subset S\subset V$})\}.\end{equation}
We prove the following theorem.

@@

\subsection{Notations}
For vectors $x,y\in \bbbr_{n}$ we say $x$ dominates $y$ if $x_i\geq y_i$ for $i= 1,\ldots,n$. For $m\times n$ matrix $A$, let $A_j$ be the $j$-th row of $A$ and $A^j$ be the $j$-th column of $A$. Let $\textbf{1}$ be the vector of all ones of a suitable dimension. For a set $S$ of vectors in $\bbbr_{n}$, $\conv(S)$ is the convex hull of all the points in $S$.

@@

Consider a formulation instance $I=(A,G,b)$, set 
\begin{equation}
S(I)= \{(x,y)\in \bbbr^{n+ p}\;:\; Ax+Gy\geq b,\; x\in \{0,1\}\},  \label{S'}
\end{equation}
and its linear relaxation
\begin{equation}
P(I) = \{(x,y)\in \bbbr^{n+ p}\;:\; Ax+Gy\geq b,\; 0 \leq x\leq 1\}. \label{P'}
\end{equation}
Also assume we are given a point $(x^*,y^*)\in P(I)$. For instance, $(x^*,y^*)$ can be the optimal solution of minimizing a cost function $cx$ over set $P$, which provides a lower bound on $\min_{(x,y)\in S(I)} cx$. In this section, we prove Theorem \ref{binaryFDT}.  One key ingredient in proving Theorem \ref{binaryFDT} is Theorem \ref{domtoIP} that we will also prove in this section.

Although the theoretical worst-case upper bound on $C$ in the statement of Theorem \ref{binaryFDT} can be very large, we will show that in practice $C$ can be really small and hence FDT can provide good LP-based approximation algorithms in many cases. We also remark that if $g_I=1$, then the algorithm will give an exact decomposition of any feasible solution.  In the remainder of this section we explain the FDT algorithm and prove Theorem \ref{binaryFDT}. For simplicity in the notation we denote $P(I),S(I),$ and $g_I$ with $P,S,$ and $g$, respectively. Let $t=|\spp(x^*)|$. We assume without loss of generality that $\spp(x^*)= \{1,\ldots,t\}$.

We begin with the following lemmas that show how the FDT algorithm branches on a variable.
\begin{lemma}\label{LPClemma}
	Given $(x',y')\in \dom(P)$ and $\ell\in \{1,\ldots,n\}$, we can find in polynomial time vectors $(\hat{x}^0,\hat{y}^0),(\hat{x}^1,\hat{y}^1)$ and scalars $\gamma_0,\gamma_1 \in [0,1]$ such that: (i) $\gamma_0 + \gamma_1  \geq \frac{ 1}{g}$, (ii) $(\hat{x}^0,\hat{y}^0)$ and $(\hat{x}^1,\hat{y}^1)$ are in  $ P$, 
		,(iii) $\hat{x}^0_\ell=0$ and $\hat{x}^1_\ell=1$, (iv) $\gamma_0 \hat{x}^0 + \gamma_1\hat{x}^1 \leq x'$.
\end{lemma}

\begin{proof} 
	Consider the following linear program which we denote by $\LPC(\ell,x',y')$. The variables of $\LPC(\ell,x',y')$ are $\gamma_0,\gamma_1$ and $(x^0,y^0)$ and $(x^1,y^1)$. 
	\begin{align}
		\LPC(\ell,x',y')\quad\quad& \max\quad \;\lambda_0+\lambda_1\\
		&\;\text{s.t.} \quad Ax^j + Gy^j\geq b\lambda_j & \mbox{ for $j=0,1$} \label{feasibility}\\
		&\;{\color{white}{\text{s.t.}} }\quad 0 \leq x^j \leq \lambda_j &\mbox{ for $j=0,1$}\label{bound}\\
		&\;{\color{white}{\text{s.t.}} }\quad x^0_\ell = 0,\; x^1_\ell =\lambda_1\label{branchcoordinate}\\
		&\;{\color{white}{\text{s.t.}} }\quad x^0 + x^1 \leq x'\label{packing}\\
		&\;{\color{white}{\text{s.t.}} }\quad \lambda_0,\lambda_1 \geq 0
	\end{align}

@@

		\begin{equation}\label{splitting}
		x'\geq \sum_{i=1}^{k}\frac{\theta_i}{g} \tilde{x}^i
		={\sum_{i\in [k]: \tilde{x}^i_\ell =0}\frac{\theta_i}{g} \tilde{x}^i}+{\sum_{i\in [k]: \tilde{x}^i_\ell =1}\frac{\theta_i}{g} \tilde{x}^i}
		\end{equation}
		For $j=0,1$, let $(x^j,y^j) = \sum_{i\in [k]:\tilde{x}^i_\ell=j} \frac{\theta_i}{g}(\tilde{x}^i,\tilde{y}^i)$. Also let $\lambda_0=\sum_{i\in [k]: \tilde{x}^i_\ell =0}\frac{\theta_i}{g}$ and $\lambda_1 = \sum_{i\in [k]: \tilde{x}^i_\ell =1}\frac{\theta_i}{g}$. Note that $\lambda_0+\lambda_1 = \frac{1}{g}$. Constraint (\ref{packing}) is satisfied by Inequality (\ref{splitting}). Also, for $j=0,1$ we have
		\begin{equation}
		Ax^j+Gy^j = \sum_{i\in[k], \tilde{x}^i_\ell = j} \frac{\theta_i}{g} (A\tilde{x}^i + G\tilde{y}^i) \geq b \sum_{i\in[k], \tilde{x}^i_\ell = j} \frac{\theta_i}{g} = b\lambda_j.
		\end{equation}
		Hence, Constraints (\ref{feasibility}) holds. Constraint (\ref{branchcoordinate}) also holds since $x^0_\ell$ is obviously $0$ and $x^1_\ell= \sum_{i\in [k]: \tilde{x}^i_\ell = 1}\frac{\theta_i}{g}= \lambda_1$. The rest of the constraints trivially hold. 
	\end{proof}
	This concludes the proof.	
\end{proof}

We now show if $x'$ in the statement of Lemma \ref{LPClemma} is partially integral, we can find solutions with more integral components.
\begin{lemma}\label{round-up}
	Given $(x',y')\in \dom(P)$, such that $x'_1,\ldots,x'_{\ell-1}\in \{0,1\}$ for some $\ell\geq 1$, we can find in polynomial time vectors $(\hat{x}^0,\hat{y}^0),(\hat{x}^1,\hat{y}^1)$ and scalars $\gamma_0,\gamma_1 \in [0,1]$ such that: (i) $\frac{ 1}{g}\leq \gamma_0 + \gamma_1  \leq 1$, (ii) $(\hat{x}^0,\hat{y}^0)$ and $(\hat{x}^1,\hat{y}^1)$ are in  $\dom( P)$, (iii) $\hat{x}^0_\ell=0$ and $\hat{x}^1_\ell=1$, (iv) $ \gamma_0\hat{x}^0 +\gamma_1 \hat{x}^1 \leq
		x'$,(v) $\hat{x}^i_j\in \{0,1\}$ for $i=0,1$ and $j=1,\ldots,\ell-1$.
\end{lemma} 
\begin{proof}
	By Lemma \ref{LPClemma} we can find $(\bar{x}^0,\bar{y}^0)$, $(\bar{x}^1,\bar{y}^1)$, $\gamma_0$ and $\gamma_1$ that satisfy (i), (ii), (iii), and (iv). We define $\hat{x}^0$ and $\hat{x}^1$ as follows. For $i=0,1$, for $j=1,\ldots,\ell-1$, let $\hat{x}^i_j= \ceil{\bar{x}^i_j}$, for $j=\ell,\ldots,t$ let $\hat{x}^i_j = \bar{x}^i_j$. We now show that $(\hat{x}^0,\bar{y}^0)$, $(\hat{x}^1,\bar{y}^1)$, $\gamma_0$, and $\gamma_1$ satisfy all the conditions. Note that conditions (i), (ii), (iii), and (v) are trivially satisfied. Thus we only need to show (iv) holds. We need to show that $\gamma_0 \hat{x}^0_j+\gamma_1\hat{x}^1_j\leq gx'_j$. If $j=\ell,\ldots,t$, then this clearly holds. Hence, assume $j\leq \ell-1$. By the property of $x'$ we have $x'_j\in \{0,1\}$. If $x'_j= 0$, then by Constraint (\ref{packing}) we have $\bar{x}^0_j = \bar{x}^1_j=0$. Therefore, $\hat{x}^i_j=0$ for $i=0,1$, so (iv) holds. Otherwise if $x'_j = 1$, then we have
	$\gamma_0\hat{x}^0_j+\gamma_1\hat{x}^1_j\leq \gamma_0+\gamma_1\leq 1\leq x'_j.$ 
	Therefore (v) holds.
\end{proof}
The FDT algorithm grows a tree similar to the classic branch-and-bound search tree for integer programs. Each node represents a partially integral vector $(\bar{x},\bar{y})$ in $\dom(P)$ together with a multiplier $\bar{\lambda}$. The solutions contained in the nodes of the tree become progressively more integral at each level. Leaves of the FDT tree contain solutions with integer values for all the $x$ variables that dominate a point in $P$. We will later see how we can turn these into points in $S$.

Let us define the FDT algorithm more formally. The algorithm maintains nodes $L_i$ in iteration $i$ of the algorithm. The nodes in $L_i$ correspond to the nodes in level $L_i$ of the FDT tree. The points in the leaves of the FDT tree, $L_t$, are points in $\dom(P)$ and are integral for all integer variables.

\begin{lemma}\label{prune}
	There is a polynomial time algorithm that produces sets $L_0,\ldots,L_t$ of pairs of $(x,y)\in \dom(P)$ together with multipliers $\lambda$ with the following properties for $i=0,\ldots,t$:
		(a) If $(x,y)\in L_i$, then $x_j \in \{0,1\}$ for $j=1,\ldots,i$, i.e. the first $i$ coordinates of a solution in level $i$ are integral, (b) $\sum_{[(x,y),\lambda]\in L_i} \lambda\geq\frac{1}{g^i}$, (c) $\sum_{[(x,y),\lambda]\in L_i}\lambda x \leq x^*$, (d) $|L_i|\leq t$.
\end{lemma}
\begin{proof}
	We prove this lemma using induction but one can clearly see how to turn this proof into a polynomial time algorithm. Let $L_0$ be the set that contains a single node (\textit{root of the FDT tree}) with $(x^*,y^*)$ and multiplier 1. It is easy to check all the requirements in the lemma are satisfied for this choice.

	Suppose by induction that we have constructed sets $L_0,\ldots,L_i$. Let the solutions in $L_i$ be $(x^j,y^j)$ for $j=1,\ldots,k$ and $\lambda_j$ be their multipliers, respectively. For each $j= 1,\ldots,k$ by Lemma \ref{round-up} (setting $(x',y')= (x^j,y^j)$ and $\ell = i+1$) we can find $(x^{j0},y^{j0}), (x^{j1},y^{j1})$ and $\lambda^0_j$, $\lambda^1_j$ with the properties (i) to (v) in Lemma \ref{round-up}. Define $L'$ to be the set of nodes with solutions $(x^{j0},y^{j0}), (x^{j1},y^{j1})$ and multipliers  $\lambda_j\lambda^0_j$, $\lambda_j\lambda^1_j$, respectively, for $j=1,\ldots,k$. It is easy to check that \iffalse{
	Notice that for each $j= 1,\ldots,k$ by property (v) in Lemma \ref{round-up} we have $x_h^{j0}, x_h^{j1}\in \{0,1\}$ for $h = 0,\ldots,i+1$. We also have
	\begin{align*}
		\sum_{[(x,y),\lambda]\in L'} \lambda & =  \sum_{j=1}^{k} \lambda_j\lambda^0_j+\lambda_j\lambda^1_j&\\
		& \geq \sum_{j=1}^{k} \frac{\lambda_j}{ g} & (\text{By property (i) in Lemma \ref{round-up}})\\
		& \geq \frac{1}{g} \sum_{[(x,y),\lambda]\in L_i}\lambda&\\
		& \geq \frac{1}{g^{i+1}}.&(\text{By induction hypothesis})	 
	\end{align*} 
	Also 
	\begin{align*}
		\sum_{[(x,y),\lambda]\in L'}\lambda x & =  \sum_{j=1}^{k} \lambda_j\big(\lambda^0_jx^{j0}+\lambda^1_jx^{j1}\big)&\\ 
		& \leq \sum_{j=1}^{k} \lambda_j x^j  & (\text{By property (iv) in Lemma \ref{round-up}})\\
		& \leq \sum_{[(x,y),\lambda]\in L_i}\lambda x&\\
		& \leq x^*.&(\text{By induction hypothesis})	 
	\end{align*} \fi set $L'$ is a suitable candidate for $L_{i+1}$, i.e. set $L'$ satisfies (a), (b) and (c). However we can only ensure that $|L'|\leq 2k\leq 2t$, and might have $|L'|>t$. We call the following linear program $\prun(L')$. Let $L' = \{[(x^1,y^1),\gamma_1],\ldots,[(x^{2k},y^{2k}),\gamma_{2k}]\}$. The variables of $\prun(L')$ is a scalar variable $\theta_j$ for each node $j$ in $L'$.  
	\begin{align}
		\prun(L')\quad\quad& \max\quad \;\sum_{j=1}^{2k} \theta_j\\
		&\;\text{s.t.} \quad \;\;\sum_{j=1}^{2k} \theta_j x^j_i\leq x^*_i &\mbox{ for $i=1,\ldots,t$} \label{packs}\\
		&\;{\color{white}{\text{s.t.}} }\quad  \;\quad\quad\theta \geq 0\label{nonneg}
	\end{align}
